Borders and Gateways: Measuring and Analyzing National AS Chokepoints

### 2018-07-30 Paper/background.tex
Added comment about needing censorship info in background
Clarified why BGP paths are different from AS graph paths

\par Finding BGP paths is more of
a challenge.\Ben[inline]{Be more clear about the difference between `Finding BGP paths' and what you have discussed above.}
Packet based simulations, wherein BGP is simulated
directly, are computationally infeasible for the scales relevant to a
global study. An accurate, but realistic, simulation technique must be
chosen to provide useful research potential in this regard.  The
BGPSim algorithm \cite{quicksand} is one such simulation technique
that is suitable for this study's purposes. BGPSim takes a set of AS
relationships as input, such as those provided by the CAIDA dataset
\cite{CAIDA}, and returns routing trees based off of these
relationships. These paths are found via a modified breadth-first
search (BFS) algorithm. The BFS adds edges to routing trees first
according to local preference (LP), then shortest path (SP), and
finally tiebreak (TB).  A resulting routing tree contains all the
equally reasonable paths (according to economic concerns) that exist
between source ASes (within the routing tree) to destination ASes (the
root of the routing tree). We find this technique suitable \Ben[inline]{Why is it suitable?} for our
purposes. We use the basic approach of BGPSim (in ways explained further in this
paper) as part of \toolname{}.

>>>>

\par Finding BGP paths is more of
a challenge. BGP paths are not simply the shortest paths available on the
AS graph. Instead, they are determined by a combination of the dynamics of
BGP updates between ASes and the local preferences of each AS to route traffic
to destinations according to the policy of the AS administrator. 
Packet based simulations, wherein BGP is simulated
directly, are computationally infeasible for the scales relevant to a
global study. An accurate, but realistic, simulation technique must be
chosen to provide useful research potential in this regard.  The
BGPSim algorithm \cite{quicksand} is one such simulation technique
that is suitable for this study's purposes. BGPSim takes a set of AS
relationships as input, such as those provided by the CAIDA dataset
\cite{CAIDA}, and returns routing trees based off of these
relationships. These paths are found via a modified breadth-first
search (BFS) algorithm. The BFS adds edges to routing trees first
according to local preference (LP), then shortest path (SP), and
finally tiebreak (TB).  A resulting routing tree contains all the
equally reasonable paths (according to economic concerns) that exist
between source ASes (within the routing tree) to destination ASes (the
root of the routing tree). We find this technique suitable \Ben[inline]{Why is it suitable?} for our
purposes. We use the basic approach of BGPSim (in ways explained further in this
paper) as part of \toolname{}.

\Ben[inline]{We need to discuss not only the background of BGP routing here, but 
also background about surveillance and censorship. We could probably shorten/tighten
the BGP stuff to make room.}
